---
title: "Creating A Project Report Template for RMarkdown with qrmdtmpl"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating A Project Report Template}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(qrmdtmpl)
```


## Disclaimer
Experiments, problems and design decisions related to coming up with a R package that allows for the seamless creation of RMarkdown reports are described and documented.


## Background
At the end of the development of a new analysis procedure, results are to be summarized in a report. 


## Alternative
According to https://usethis.r-lib.org/reference/use_rmarkdown_template.html a new RMarkdown template can be created by 

``` r 
usethis::use_rmarkdown_template(template_name = "Qualitas AG Project Report", 
                                template_dir  = 'quagprojectreport',
                                template_description = 'Report for FB-ZWS Projects for Qualitas AG')
```

This creates a subdirectory named 'quagprojectreport' which contains 

* template.yaml: file with Information about the template
* subdirectory 'skeleton': This directory contains the file 'skeleton.Rmd' which is the template for the RMarkdown document. 

For any given template, the above command must only be run once. After that the template can be adapted to the requirements that must be fullfilled for the documents that are later to be generated from this template.


## Beamer Template
The beamer template was created with 

``` r
usethis::use_rmarkdown_template(template_name = "Empty Beamer Slides",
template_dir  = 'quagbeamer',
template_description = 'Empty Beamer Slides for a Presentation')

```


## Bookdown Template
We start to create a bookdown based template using the following command

```{r, echo=TRUE, eval=FALSE}
usethis::use_rmarkdown_template(template_name = "Bookdown Skeleton Project", 
                                template_dir = 'qbookdown',
                                template_description = 'Bookdown Skeleton Project for Qualitas AG',
                                template_create_dir = TRUE)
```


## Tufte Report
The following command was used to create a templated that is based on a Tufte report.

```{r, echo=TRUE, eval=FALSE}
usethis::use_rmarkdown_template(template_name = "Tufte Report Skeleton",
                                template_dir = "qtufte",
                                template_description = "Tufte Report for Qualitas AG",
                                template_create_dir = TRUE)
```


## Bookdown pdf_document2
 A pdf document with citation and references to titles, tables and equations is best created by the format `bookdown::pdf_document2`. 
 
```{r, echo=TRUE, eval=FALSE}
usethis::use_rmarkdown_template(template_name = "Bookdown PDF Document",
                                template_dir = "qbdpdf2",
                                template_description = "Bookdown PDF Document", 
                                template_create_dir = TRUE)
```
 
